\subsection{Functional Requirements} % (fold)
\label{sub:functional_requirement}
\begin{enumerate}
	\item Many Users: for each project, multiple participants can join the project, owner/owners of the project will be the administrator of his project. the advisor(e.g teacher) will get special attention from student(administrator) comparing to the other members;
	\item Template: User must chose a template from list or upload its own template
	\item Schedule: Schedule for writing report according to type of the template  (Sub schedule each section e.g introduction , etc).
	\item Propose Suggestions/Tips: The system should be able to suggest tips and information to the user on how to write sections.
	\item Send/Receive Feedback: Feedback on report which will be send by reviewer(or other users) and which will be received by student.
	\item Done/Discard: When a user is done/discarding the suggestion/feedback, he should be able to notify that to the system and all other users. 
	\item Upload Document: Ability to upload the document.
	\item In built Chat mechanism: To track the feedback of advisor and follow up the result of conversations. 
	\item Versioning : keeping track of versions of publications of user.
	\item Logging : save user records in a separate log file for usage analytics.
\end{enumerate}

% subsection functional_requirement (end)
\subsection{Technical Requirements} % (fold)
\label{sub:technical_requirements}
\begin{enumerate}
	\item Mobile Support for Android/IOS
	\item Campus ID authentication: login with TUDelft netid
	\item Open source
 	\item Fully Tested System 
	 
\end{enumerate}


% subsection technical_requirements (end)
\subsection{Usability Requirements} % (fold)
\label{sub:usability_requirements}
\begin{enumerate}
	\item System must be fully functional on modern web browsers
	\item Efficiency of use: System must facilitate efficiency of use for the user by providing information on the fly for the context
	\item Intuitiveness: User Interface must be intuitive and easy to use
\end{enumerate}
% subsection usability_requirements (end)