\chapter{Info Sheet}    
\textbf{Virtual Assistant web application\\}
\textbf{\small{TU Delft library\\}}
\textbf{Presentation Date: } 13 March 2015\\ 
\bigskip
\textbf{Description: \\}
 The practise of writing academic articles can be quite troublesome for researchers and students. They often encounter hurdles in terms of both writing 
 and planning their article layout. This problem was pointed out by the TU Delft library R \& D department. They provided us with the idea of a 
 'Virtual Assistant' that would guide researchers throughout their writing process. During the research phase of this project, we analyzed various tools and brainstormed the best available options 
 and optimal solutions. The biggest challenge for us here was keeping the balance between time and quality within the 12 weeks of the project cycle. 
 Our final choice revolved around fast prototyping, as the client (TU Library) prefered a proof-of-concept over a fully finished deployable application. 
 Making use of the Scrum conventions has helped us to achieve proper planning and to define each feature in detail. No major problems related to the 
 main features of the project were encountered, however some difficulties arose as illustrated within the final report. As a final remark, certain 
 additional features have been left out for future version due to time limitation.\\

 \bigskip
 \textbf{Members of the project team :\\}
  \textit{Member 1: \\}
	Name: Arnaud Hambenne\\
	Interests: Front-end development, Scalability, User Interaction\\ 
	Role \& Contribution: Product Owner, Developer\\
   \textit{Member 2: \\}
   Name: Soheil Jahanshahi\\
   Interests: Back-end development, Scrum, Optimization, Pattern Design, Algorithms , Software Testing, Web Services.\\ 
   Role \& Contribution : Scrum Master, Developer\\
 The complete list of contributions can be viewed on the project's \href{https://github.com/solix/Virtual.Assistant.TU.Library/tree/master/Documentation/Sprint%20Reports}{Github page} under sprint report folder.\\\\
\textbf{Client ,Coach \\}
\textit{Name and affiliation of the client : } Mr. Babak Dehghenpour et al., R \& D group, TU Library\\
\textit{Name and affiliation of the project coach:} A. Bacchelli , SERG group, TU Delft \\\\
\textbf{Contacts: \\}
\textit{Contact person 1: } Soheil Jahanahsahi, E: soheil.jahanshahi@gmail.com \\
\textit{Contact person 2: } Arnaud Hambenne, E: a.hambenne@gmail.com 


