\section{SIG feedback} % (fold)
Throughout the implementation process of the application, the Software Improvement Group (SIG) has provided us with constructive feedbacks in terms of 
maintenance and quality, and also gave us some guidelines about how to improve the code in general. The application's code has been submitted at two 
stages during the development: Mid-review and final review.\\

By the end of the sixth sprint (the middle of the project), a first submission was performed after which SIG provided us with their initial feedback 
about the code. They stated that the code achieved a score of 4 out of 5 stars in their maintenance model, which is above average. The reason that the 
code did not achieve a full score was due component imbalance, duplication and unit size. As a sidenote, they also found the component structure in the 
file system unclear, which would make it difficult for other developers to gain a high level understanding of the application architecture.\\

For the second submission, the code was adapted according to SIG's feedback. The main goal for this submission was to abide to their guidelines, whilst 
contuously improving the application in terms of lines of code, files and components, which were growing simultaneously. Having applied SIG's feedback 
to the application has helped to improve maintainability, and improved the overall code quality.\\
 
As per our coach's request, the test coverage percentage had to be increased up to 70\%. The unit size was kept as small as possible, mainly by avoiding 
code duplication, however it turned out this was not always possible. At the time of the final submission to SIG, the score did not improve dispite the 
changes made compared to the previous submission. The main reason for this was limited time and sharp deadlines which shifted the focus from code 
cleanup and testing to implementing features that functions properly. Moreover, APIs where employed locally which were not self-written, yet still had 
to be included as a part of the file system for the application to function properly. On the bright side however, most of the duplicated code was 
removed, test coverage had been increased and the file structure was refactored in order to provide a more clear overview of the MVC architecture.\\ 